% !TEX root = ../odd_cartan.tex

\section{Effective constructions}\label{s:effective}

\noindent We now turn to the effective construction of natural Cartan relators for the cochains of simplicial sets, or, more generally, Barratt--Eccles algebras.

\subsection{The construction $\EE$}

Let $\Set$ and $\sSet$ denote the categories of sets and simplicial sets respectively.
The symmetric monoidal functor $\EE \colon \Set \to \sSet$ is defined on an object $X$ by $\EE X_n = X^{n+1}$ with
\[
\begin{split}
	\face_i(x_0,\dots,x_n) &= (x_0,\dots,\widehat{x}_i,\dots,x_n), \\
	\dege_i(x_0,\dots,x_n) &= (x_0, \dots, x_i, x_i, \dots, x_n),
\end{split}
\]
and on a morphism $h$ by
\[
(\EE h)(x_0,\dots,x_n) = (h(x_0),\dots,h(x_n)).
\]
If $X$ is equipped with a group action then $\EE X$ is as well, defined by
\[
(x_0,\dots,x_n) \cdot \gamma = (x_0 \gamma, \dots, x_n \gamma).
\]
Notice that in this case each $(\EE X)_n$ is a set with a group action and each $\face_i$ and $\dege_i$ is equivariant.

\subsection{The Barratt--Eccles operad}\label{ss:barratt-eccles}

The usual block permutation map
\[
\bcomp_{\sym} \colon \sym_r \times \sym_{s_1} \times \cdots \times \sym_{s_r} \to \sym_{s_1+\dots+s_r}
\]
provides $\sym = \{\sym_r\}_{r>0}$ with the structure of an operad in $\Set$.

The simplicial Barratt--Eccles operad $\rE\sym$ is obtained by applying the functor $\EE$ to the operad $\sym$.
We denote its composition by
\[
\bcomp_{\rE\sym} \colon
\rE\sym_r \times \rE\sym_{s_1} \times\dots\times \rE\sym_{s_r} \to
\rE\sym_{s_1+\dots+s_r}.
\]

The (algebraic) Barratt--Eccles operad $\BE$ is defined by $\BE(r) = \chains\EE\sym_r$ with composition given by
\[
\bcomp_{\BE} \defeq \bcomp_{\EE} \comp \EZ \colon \BE(r) \ot \BE(s_1) \ot\dotsb\ot \BE(s_r) \to \BE(s_1+\dots+s_r).
\]
The Barratt--Eccles operad is an $E_\infty$-operad.
For any simplicial set $X$, Berger and Fresse \cite{berger2004combinatorial} explicitly constructed a natural operad morphism
\[
\phi \colon \BE \to \End(\cochains(X))
\]
on its (normalized) cochains.
Since only the existence of this effective construction will be used here, we refer to the original source for details, and to the specialized computer algebra system \texttt{ComCH} for an implementation.

\begin{remark*}
	All operations $\cochains(X)^{\ot r} \to \cochains(X)$ resulting from the map $\phi$ are obtained as compositions of the duals of the Alexander--Whitney diagonal and a join map \cite{medina2020prop1, medina2021prop2}.
\end{remark*}

\subsection{May--Steenrod structure on Barratt--Eccles algebras}\label{ss:may-steenrod on barratt-eccles}

To provide the cochains of simplicial sets, or more generally any $\BE$-algebra, with a natural May--Steenrod structure, we need to define a $\cyc$-equivariant quasi-isomorphism
\[
\iota \colon \cW \to \BE.
\]
We now recall from \cite{medina2021may_st} a closed form formula for one such map which factors through the $\cyc$-module
\[
\cC \defeq \{\chains\EE\cyc_r\}_{r>0}.
\]
For $r,n\in\N$, let
\[
\iota(e_{n}) =
\begin{cases}
	\displaystyle{\sum_{s_1, \dots, s_m}} \big(0, {s_1}, {s_1+1}, {s_2}, {s_2+1}, \dots, {s_{m}}, {s_{m}+1} \big) & n = 2m, \\
	\displaystyle{\sum_{s_1, \dots, s_m}} \big(0, 1, {s_1}, {s_1+1}, \dots, {s_{m}}, {s_{m}+1} \big) & n = 2m+1,
\end{cases}
\]
where the sum is over all $s_1, \dots, s_m \in \{0, \dots, r-1\} \cong \cyc_r$.
Please consult \cref{f:small values of psi} for the simplest examples.
We remark that the number of basic summands above for $r$ and $n = 2m, 2m + 1$ is $(r-1)^m$.

\begin{table}
	\centering
	\input{aux/table}
	\caption{The elements $\psi^r(e_n)$ for small values of $r$ and $n$.}
	\label{f:small values of psi}
\end{table}

Given a Barratt--Eccles algebra $\phi \colon \BE \to \End(A)$ we will consider $A$ as a May--Steenrod complex with the structure defined by $\phi$ and $\iota$.

\begin{remark*}
	In \cite{medina2021may_st}, the map $(\phi \comp \iota)(e_i) \colon A^{\ot r} \to A$ is referred to as the cup-$(r,i)$ product of the May--Steenrod complex $A$.
	For simplicial sets, a natural $\cyc_p$-equivariant chain map $\cW(p) \to \End(\cochains(X))(p)$ is constructed in \cite{medina2024connected}, for $p$ prime, using a Poincar\'e duality algebra structure on the chains of standard augmented simplices.
	The resulting maps $\cochains(X)^{\ot p} \to \cochains(X)$ agree with the cup-$(p,i)$ products only for $p=2$, where they recover the axiomatically characterized cup-$i$ products of Steenrod \cite{steenrod1947products, medina2023fast_sq, medina2022axiomatic}, and for $p=3$, but they differ for higher primes.
\end{remark*}

\subsection{Main diagram}

Our goal is to construct a natural Cartan relator for $\BE$-algebras, that is to say, a natural $\cyc$-equivariant homotopy $H \colon \cW \to \End(A)^\ev$ from $G$ to $\tau \comp F$ for any $\BE$-algebra $A$.
We will do so by constructing $\cyc$-equivariant chain homotopies $K_1$, $K_2$, and $K_3$ making, for each $r>0$, the following diagram commute:
\begin{equation}\label{d:big diagram}
	\input{sec/diagram}
\end{equation}
where $e \in \sym_2$ is the identity element denoting, abusively, the element $(e) \in \BE(2)_0$.
Explicitly, $K_1^r$ and $K_2^r$ are $g$-equivariant whereas $K_3^r$ is $\cyc_r$-equivariant with the diagonal action on the target.

\begin{lemma}\label{l:main_diag}
	In diagram \eqref{d:big diagram}, the top composition agrees with $\tau \comp F^r$ and the bottom one does so with $G^r$.
\end{lemma}

\begin{proof}
	Let us write $\cO$ instead of $\End(A)$ for a Barratt--Eccles algebra $A$ as in \cref{ss:cartan_relators}, where the maps $\tau \comp F_\psi^r$ and $G_\psi^r$ are defined, and omit the superscripts of $\psi^r$ and $\psi_0^2$.
	The first claim is equivalent to the commutativity of
	\[
	\begin{tikzcd}
		&
		\BE(r) \arrow[d,"\phi"] \arrow[r,"\id\, \ot\, e^{\ot r}"] &[10pt]
		\BE(r) \ot \BE(2)^{\ot r} \arrow[d,"\phi^{\ot 3}"] \arrow[r,"\bcomp_{\BE}"] &
		\BE(2r) \arrow[d,"\phi"] \arrow[r,"\tau"] &
		\BE(2r) \arrow[d,"\phi"] \\
		\cW(r) \arrow[r,"\psi"] \arrow[ur, in=180, out=60,"\iota"] &
		\cO(r) \arrow[r,"\id\, \ot\, \psi_0^{\ot r}"] &
		\cO(r) \ot \cO(2)^{\ot r} \arrow[r,"\bcomp_{\cO}"] &
		\cO(2r) \arrow[r,"\tau"] &
		\cO(2r)
	\end{tikzcd}
	\]
	where the bottom composition is $\tau \comp F_\psi^r$\,, whereas the second is equivalent to the commutativity of
	\[
	\begin{tikzcd}
		&[-10pt] &
		\BE(r)^{\ot2} \arrow[d,"\phi^{\ot 2}"] \arrow[r,"e\,\ot\,\id"] &[10pt]
		\BE(2) \ot \BE(r)^{\ot2} \arrow[d,"\phi^{\ot 3}"] \arrow[r,"\bcomp_{\BE}"] &
		\BE(2r) \arrow[d,"\phi"] \\
		\cW(r) \arrow[r,"\Delta"] &
		\cW(r)^{\ot 2} \arrow[r,"\psi^{\ot 2}"] \arrow[ur, in=180, out=60,"\iota^{\ot 2}"] &
		\cO(r)^{\ot 2} \arrow[r,"\psi_0\,\ot\,\id"] &
		\cO(2) \ot \cO(r)^{\ot 2} \arrow[r,"\bcomp_{\cO}"] &
		\cO(2r),
	\end{tikzcd}
	\]
	where the bottom composition is $G_\psi^r$\,.
	Both of these diagrams are commutative since $\phi$ is an operad map and, by definition, $\psi = \phi \comp \iota$.
\end{proof}

\subsection{Comparing $F$ and $\phi \comp \chains\EE(f) \comp \iota$}

Let us focus on the following part of Diagram~\eqref{d:big diagram}:
\[
\begin{tikzcd}[row sep=small]
	&[-10pt]\BE(r) \arrow[r,"\id \, \ot e^{\ot r}"] &[5pt]
	\BE(r) \ot \BE(2)^{\ot r} \arrow[d,"\bcomp_{\BE}"] &[-20pt] \\ &
	&\BE(2r) \arrow[d, "\tau"] & \\
	\cW(r) \arrow[r,"\iota"] &
	\cC(r) \arrow[uu,hook] \arrow[r,"\tau \comp \chains\EE(f)"] &
	\BE(2r) \arrow[r,"\phi"] & \End(A)^\ev(r).
\end{tikzcd}
\]
Its commutativity is equivalent to the following.

\begin{lemma}\label{l:K0}
	For any Barratt--Eccles algebra with its canonical May--Steenrod structure, we have
	\[
	\tau \comp F_\psi = \phi \comp \tau \comp \chains\EE(f) \comp \iota.
	\]
\end{lemma}

\begin{proof}
	Consider the diagram
	\[\label{d:F and f}
		\begin{tikzcd}[column sep=small,row sep=tiny]
			&& \chains\EE\sym_r \ot (\chains\EE\sym_2)^{\ot r}
			\arrow[dr,"\bcomp_{\BE}",out=0,in=120]
			\arrow[dd,"\EZ"] &&[10pt] \\
			\cW(r) \arrow[r,"\iota"] &
			\chains\EE\cyc_r
			\arrow[ur,"\id \, \ot e^{\ot r}", out=60,in=180]
			\arrow[dr,"\chains\EE(\id \times e^r)"',out=-60,in=180]
			& & \chains\EE\sym_{2r} \arrow[r,"\phi\;\comp\,\tau"] &
			\End(A)(2r). \\
			&& \chains\EE(\sym_r \times \sym_2^r)
			\arrow[ur, "\chains\EE(\bcomp_{\sym})"', out=0,in=-120]
			&
		\end{tikzcd}
	\]
	Its top composition is $\tau \comp F_\psi^r$ as in the proof of \cref{l:main_diag}.
	Its bottom composition is $\phi \comp \tau \comp \chains\EE(f) \comp \iota$ since $f \colon \cyc_r \hookrightarrow \sym_r \xra{\id \times e^r} \sym_r \times \sym_2^r \xra{\bcomp_{\sym}} \sym_{2r}$.
	The right side of the diagram commutes by the definition of $\bcomp_\BE$.
	The left side of the diagram commutes because, if $v$ is $0$-simplex, the $\EZ$ map $\chains(X) \ot v \to \chains(X \times v)$ is trivially an isomorphism, taking $x \ot v$ to $x \times \mathrm{s}(v)$, where $\mathrm{s}(v)$ is the unique degenerate simplex of $v$ whose whose dimension agrees with that of $x$.
\end{proof}

\subsection{The homotopy $K_1$}\label{ss:K1}

Let us focus on the following part of Diagram \eqref{d:big diagram}:
\[
\begin{tikzcd}[column sep=large]
	\cC(r)
	\arrow[r,bend left,"\tau \comp \chains\EE(f)"]
	\arrow[r,bend right,"\chains\EE(g)"']
	\arrow[r,phantom,"K_1^r"]
	& \BE^\ev(r).
\end{tikzcd}
\]
We will show that it is homotopy commutative.
More precisely, let $K_1 \colon \cC \to \BE^\ev$ be defined by
\[
K_1(a_0,\dots,a_n) =
\sum_{i=0}^n \ (-1)^i (g(a_0), \dots, g(a_i), f(a_i) \tau, \dots, f(a_n) \tau).
\]

\begin{lemma}\label{l:K1}
	$K_1 \colon \cC \to \BE^\ev$ is a $\cyc$-equivariant homotopy from $\chains\EE(g)$ to $\tau \comp \chains\EE(f)$.
\end{lemma}

\begin{proof}
	We need to show that
	\[
	\bd \comp K_1 + K_1 \comp \bd = \tau \comp \chains\EE(f) - \chains\EE(g),
	\qquad
	K_1 \comp \rho = g(\rho) \comp K_1.
	\]
	We will simplify notation and denote $g(a_i)$ and $f(a_i)$ simply as $g_i$ and $f_i$.
	\begin{align*}
		\bd \comp K_1(a_0,\dots,a_n) &=
		\sum_{i \geq j} \sum_{i=0}^n \ (-1)^{i+j} (g_0, \dots, \widehat{g_j}, \dots, g_i, f_i\tau, \dots f_n \tau) \\ & -
		\sum_{i \leq j} \sum_{i=0}^n \ (-1)^{i+j} (g_0, \dots, g_i, f_i \tau, \dots, \widehat{f_j\tau}, \dots, f_n \tau)
	\end{align*}
	and
	\begin{align*}
		K_1 \comp \bd(a_0,\dots,a_n) &=
		\sum_{i<j} \sum_{j=0}^n \ (-1)^{i+j} (g_0, \dots, g_i, f_i\tau, \dots, \widehat{f_j\tau}, \dots, f_n \tau) \\ & -
		\sum_{i > j} \sum_{j=0}^n \ (-1)^{i+j} (g_0, \dots, \widehat{g_j}, \dots, g_i, f_i\tau, \dots f_n \tau).
	\end{align*}
	Therefore,
	\begin{align*}
		\bd K_1(a_0,\dots,a_n) &=
		\sum_{i=0}^n (g_0, \dots, \widehat{g_i}, f_i\tau, \dots, f_n \tau) -
		(g_0, \dots, g_i, \widehat{f_i\tau}, \dots, f_n \tau) \\ &=
		(f_0\tau, \dots, f_n\tau) - (g_0, \dots, g_n) \\ &=
		(\tau \comp \chains\EE(f) - \chains\EE(g))(a_0,\dots,a_n).
	\end{align*}
	Recall from \cref{l:conjugated} that $f \comp \tau = \tau \comp g$, hence
	\begin{align*}
		(K_1 \comp \rho) &(a_0,\dots,a_n) \\ &=
		\sum_{i=0}^n \ (-1)^i (g(a_0 \rho), \dots, g(a_i\rho), f(a_i\rho)\tau, \dots, f(a_n\rho) \tau) \\ &=
		\sum_{i=0}^n \ (-1)^i (g(a_0) g(\rho), \dots, g(a_i)g(\rho), f(a_i)\tau g(\rho), \dots, f(a_n)\tau g(\rho)) \\ &=
		(g(\rho) \comp K_1) (a_0,\dots,a_n).\qedhere
	\end{align*}
\end{proof}

\subsection{The homotopy $K_2$}

Let us focus on the following part of Diagram~\eqref{d:big diagram}:
\[
	\begin{tikzcd}[row sep=small]
		\cC(r)
		\arrow[r,"\chains\EE(g)"]
		\arrow[d,"\Delta_{\AW}"']
		\arrow[ddr,phantom,"K_2^r",shift left=0pt]
		&[5pt] \BE(2r) \\
		\cC(r)^{\ot 2}
		\arrow[d,hook] & \\
		\BE(r)^{\ot 2}
		\arrow[r,"e\, \ot\, \id"]
		& \BE(2) \ot \BE(r)^{\ot 2}.
		\arrow[uu,"\bcomp_\BE"']
	\end{tikzcd}
\]
We will construct a $g$-equivariant map $K_2^r$ making it homotopy commutative for each $r$.
Specifically, let $K_2 \colon \cC \to \BE^\ev$ be the composition
\[
K_2 = \chains(\bcomp_{\EE\sym}) \comp \Shi \comp \chains\EE(e \times \id) \comp \chains\EE(\rD).
\]

\begin{lemma}\label{l:K2}
	$K_2$ is a $\cyc$-equivariant homotopy from $\bcomp_{\BE} \comp (e \ot \id) \comp \Delta_{\AW}$ to $\chains\EE(g)$.
\end{lemma}

\begin{proof}
	We need to prove the following identities:
	\[
	\bd K_2 = \chains\EE(g) - \bcomp_{\BE} \comp (e \ot \id) \comp \Delta_{\AW},
	\qquad
	K_2 \comp \rho = g(\rho) \comp K_2,
	\]
	where $\bd$ denotes the boundary of $\cyc$-equivariant maps from $\cC$ to $\BE^\ev$.
	Since $\bd \Shi = \id - \EZ \comp \AW$ we have that
	\[
	\bd K_2 =
	\chains(\bcomp_{\EE\sym}) \comp \chains\EE(e \times \id) \comp \chains\EE(\rD) -
	\chains(\bcomp_{\EE\sym}) \comp \EZ \comp \AW \comp \chains\EE(e \times \id) \comp \chains\EE(\rD).
	\]
	Recall that $g$ is the composition $\cyc_r \hookrightarrow \sym_r \xra{\rD} \sym_r^{\times 2} \xra{e \times \id} \sym_2 \times \sym_r^{\times 2} \xra{\bcomp_{\sym}} \sym_{2r}$\,, and that $\bcomp_{\BE} = \chains(\bcomp_{\EE\sym}) \comp \EZ$, so
	\[
	\bd K_2 =
	\chains\EE(g) -
	\bcomp_{\BE} \comp \AW \comp \chains\EE(e \times \id) \comp \chains\EE(\rD).
	\]
	Recall that $\Delta_{\AW} = \AW \comp \chains\EE(\rD)$.
	Since $\AW(x \times y \times z) = v \ot \AW(y \times z)$ for any triple of simplices $x,y,z$ with $x = v$ a $0$-simplex or the image of one via a degeneracy maps $x = \mathrm{s}(v)$, we have
	\[
	\bd K_2 =
	\chains\EE(g) -
	\bcomp_{\BE} \comp \chains\EE(e \times \id) \comp \Delta_{\AW}
	\]
	as stated in the first identity to prove.
	This computation is summarized in the following diagram:
	\[
	\hspace*{-4pt}
	\begin{tikzcd}
		\chains\EE\cyc_r
		\rar[hook]
		\arrow[dr,in=180,out=-90,"\Delta_{\AW}"]
		&[-20pt]
		\chains\EE\sym_r
		\rar["\chains\EE(\rD)"] &[-10pt]
		\chains\EE\sym_r^{\times 2}
		\rar["\chains\EE(e \times \id)"]
		\dar["\AW"'] &[7pt]
		\chains\EE(\sym_2 \times \sym_r^{\times 2})
		\rar["\chains(\bcomp_{\EE\!\sym})"]
		\dar["\AW"']
		\drar["\id",out=-10,in=150] &[-5pt]
		\chains\EE\sym_{2r} \\ &
		(\chains\EE\cyc_r)^{\ot 2}
		\arrow[r,hook] &
		\chains\EE\sym_r^{\ \ot 2}
		\rar["e \,\ot\, \id"] &
		\chains\EE\sym_2 \ot \chains\EE\sym_r^{\ \ot 2}
		\rar["\EZ"]
		\uar["\Shi",phantom,shift right=30pt] &
		\chains\EE(\sym_2 \times \sym_r^{\times 2}).
		\uar["\chains(\bcomp_{\EE\!\sym})"']
	\end{tikzcd}
	\]

	To check the equivariance condition we recall that face and degeneracy maps are $\cyc_r$-equivariant between sets of simplices in $\EE\cyc_r$, and that $\Shi$ is expressed as a sum of compositions of these.
	Therefore,
	\begin{align*}
		K_2 \comp \rho &=
		\chains(\bcomp_{\EE\sym}) \comp \Shi \comp \chains\EE(e \times \id) \comp \chains\EE(\rD) \comp \rho \\ &=
		\chains(\bcomp_{\EE\sym}) \comp (\id \times \rho \times \rho) \comp \Shi \comp \chains\EE(e \times \id) \comp \chains\EE(\rD) \\ &=
		g(\rho) \comp \chains(\bcomp_{\EE\sym}) \comp \Shi \comp \chains\EE(e \times \id) \comp \chains\EE(\rD) \\ &=
		g(\rho) \comp K_2. \qedhere
	\end{align*}
\end{proof}

\subsection{The homotopy $K_3$}\label{ss:coproduct}

Let us focus on the following part of Diagram~\eqref{d:big diagram}:
\[
\begin{tikzcd}
	\cW(r)
	\arrow[r,"\iota"]
	\arrow[d,"\Delta"']
	\arrow[dr,phantom,"K_3^r"]
	& \cC(r)
	\arrow[d,"\Delta_{\AW}"] \\
	\cW(r)^{\ot 2}
	\arrow[r,"\iota^{\ot 2}"']
	& \cC(r)^{\ot 2}
\end{tikzcd}
\]
We will construct a $g$-equivariant map $K_3^r$ making it homotopy commutative for each~$r$.

Using the bijection $\cyc_r \cong \set{0,\dots,r-1}$, denote by $\alpha(s_1,\dots,s_\ell)$ the number of increasing consecutive pairs $s_i < s_{i+1}$ in a sequence $(s_1,\ldots,s_\ell)$ of elements of $\cyc_r$.
For example, to compute $\alpha(2,4,1,3,1,0,4)$ we count the number of increasing consecutive pairs $(2,4),(1,3),(0,4)$, which is $3$, whereas $\alpha(3,1,0,2,4,3) = 2$ with increasing consecutive pairs $(0,2)$ and $(2,4)$.

Let $K_3^r \colon \cW(r) \to \cC(r)^{\ot 2}$ be defined by equivariantly extending the following assignment on basis elements:
\[
\begin{split}
	K_3^r(e_{2i}) &= \sum \, \alpha(s_1,\ldots,s_j,t_1)\cdot\varphi^{\mathrm{even}}(s_1,\dots,s_j;t_1,\dots,t_k), \\
	K_3^r(e_{2i+1}) &= -\sum \, \alpha(s_1-1,\ldots,s_j-1,t_1-1)\cdot \varphi^{\mathrm{odd}}(s_1,\dots,s_j;t_1,\dots,t_k),
\end{split}
\]
where the sums are taken over all $s_1,\dots,s_j,t_1,\dots,t_k \in \cyc_r$ with $j+k = i+1$ and
\begin{align*}
	\varphi^{\mathrm{even}}(s_1,\dots,s_j&;t_1,\dots,t_k) \\ &=
	(0,s_1,s_1+1,\dots,s_j,s_j+1) \ot (t_1,t_1+1,\dots,t_k,t_k+1), \\
	\varphi^{\mathrm{odd}}(s_1,\dots,s_j&;t_1,\dots,t_k) \\ &=
	(0,1,s_1,s_1+1,\dots,s_j,s_j+1) \ot (t_1,t_1+1,\dots,t_k,t_k+1).
\end{align*}
For example, the summand indexed by $(s_1,\ldots,s_6;t_1,t_2,t_3) = (2,4,1,3,1,0;4,2,1)$ in $K_3^5(e_{16})$ is
\[
3 \cdot (0,2,3,4,0,1,2,3,4,1,2,0,1) \otimes (4,0,2,3,1,2),
\]
whereas the summand indexed by $(s_1,\ldots,s_5;t_1,t_2) =(4,2,1,3,0;4,1)$ in $K_3^5(e_{13})$ is
\[
-2 \cdot (0,1,4,0,2,3,1,2,3,4,0,1) \otimes (4,0,1,2).
\]
Please consult \cref{f:small values of K} for a the first few non-trivial examples.

\begin{table}
	\centering
	\input{aux/table2}
	\caption{The elements $K_3(e_n)$ for small values of $r$ and $n$. For $r=2$ or $n<2$ all vanish. Notice that the indices are flipped with respect to \cref{f:small values of psi} for spacing reasons.}
	\label{f:small values of K}
\end{table}

We remark that the numbers $\alpha(s_1,\ldots,s_\ell)$ are always non-negative, and therefore all non-trivial summands in $K_3^r(e_{2i})$ have positive coefficients and all non-trivial summands in $K_3^r(e_{2i+1})$ have negative coefficients.
Observe also that the summands in $K_3^r(e_{2i})$ are in bijection with the summands in $K_3^r(e_{2i+1})$ and the bijection changes the sign of the coefficient of each summand.

\begin{lemma}\label{l:K3}
	$K_3$ is a $\cyc$-equivariant homotopy from $\Delta_{\AW} \comp \iota$ to $(\iota \ot \iota) \comp \Delta$.
\end{lemma}

\begin{proof}
	We devote \cref{s:postponed} to the proof of this statement.
\end{proof}

\subsection{Main construction}

With Diagram~\eqref{d:big diagram} in mind, let us define $H \colon \cW \to \End(A)^\ev$ as the composition
\[
H = \phi \comp K_1 \comp \iota \ +\ \phi \comp K_2 \comp \iota \ -\ \phi \comp \bcomp_{\BE} \comp (e \ot \id) \comp K_3.
\]

\begin{theorem}
	$H$ is a natural Cartan relator for Barratt--Eccles algebras.
\end{theorem}

\begin{proof}
	Recall that if $h$ is an element in a $\Hom$ complex, then $\bd h$ is defined as usual as $\bd \comp h - (-1)^{\deg(h)} h \comp \bd$.
	Combining \cref{l:main_diag,l:K0,l:K1,l:K2,l:K3} we have
	\begin{align*}
		\bd H &=
		\phi \comp \bd K_1 \comp \iota \ +\
		\phi \comp \bd K_2 \comp \iota \ -\
		\phi \comp \bcomp_{\BE} \comp (e \ot \id) \comp \bd K_3 \\ &=
		\phi \comp \chains\EE(f) \comp \iota \ +\
		\phi \comp (-\chains\EE(g) + \bd K_2) \comp \iota \ -\
		\phi \comp \bcomp_{\BE} \comp (e \ot \id) \comp \bd K_3 \\ &=
		\tau \comp F - \phi \comp \bcomp_{\BE} \comp (e \ot \id) \comp (\Delta_{\AW} \comp \iota + \bd K_3) \\ &=
		\tau \comp F - G,
	\end{align*}
	and, since $\bcomp_{\BE} \comp (\id \ot \rho \ot \rho) = g(\rho) \comp \bcomp_{\BE}$\,,
	\[
	H \comp \rho = g(\rho) \comp H. \qedhere
	\]
\end{proof}